Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-04 paper.qmd
Updated Figure 11

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.6,
  axis_pos_y = -0.63,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    alpha = 0.4,
    linewidth = 0.1) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2),
    label=rownames(axes), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.84, 0.84)) +
  ylim(c(-0.84, 0.84)) +
  interior_annotation("a2", 
                      position = c(0.08, 0.9),
                      cex = 2)
```

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.6,
  axis_pos_y = -0.63,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    alpha = 0.4,
    linewidth = 0.1) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.83, 0.83)) +
  ylim(c(-0.83, 0.83)) +
  interior_annotation("b2", 
                      position = c(0.08, 0.9),
                      cex = 2)
```

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.6,
  axis_pos_y = -0.63,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_pacmap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000",
    alpha = 0.4,
    linewidth = 0.1) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2, label=rownames(axes)),
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.83, 0.83)) +
  ylim(c(-0.83, 0.83)) +
  interior_annotation("c2",
                      position = c(0.08, 0.9),
                      cex = 2)

>>>>

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.72,
  axis_pos_y = -0.72,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    alpha = 0.4,
    linewidth = 0.1) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2),
    label=rownames(axes), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.89, 0.89)) +
  ylim(c(-0.89, 0.89)) +
  interior_annotation("a2", 
                      position = c(0.08, 0.9),
                      cex = 2)
```

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.72,
  axis_pos_y = -0.72,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    alpha = 0.4,
    linewidth = 0.1) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.89, 0.89)) +
  ylim(c(-0.89, 0.89)) +
  interior_annotation("b2", 
                      position = c(0.08, 0.9),
                      cex = 2)
```

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.72,
  axis_pos_y = -0.72,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_pacmap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000",
    alpha = 0.4,
    linewidth = 0.1) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2, label=rownames(axes)),
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.89, 0.89)) +
  ylim(c(-0.89, 0.89)) +
  interior_annotation("c2",
                      position = c(0.08, 0.9),
                      cex = 2)
